---
title: "betaDelta"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![CRAN Status](https://www.r-pkg.org/badges/version/betaDelta)](https://cran.r-project.org/package=betaDelta)
[![R-Universe Status](https://jeksterslab.r-universe.dev/badges/betaDelta)](https://jeksterslab.r-universe.dev)
[![R-CMD-check](https://github.com/jeksterslab/betaDelta/workflows/R-CMD-check/badge.svg)](https://github.com/jeksterslab/betaDelta/actions)
[![test-coverage](https://github.com/jeksterslab/betaDelta/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/jeksterslab/betaDelta/actions/workflows/test-coverage.yaml)
[![lint](https://github.com/jeksterslab/betaDelta/actions/workflows/lint.yaml/badge.svg)](https://github.com/jeksterslab/betaDelta/actions/workflows/lint.yaml)
[![codecov](https://codecov.io/gh/jeksterslab/betaDelta/branch/main/graph/badge.svg?token=KVLUET3DJ6)](https://codecov.io/gh/jeksterslab/betaDelta)
<!-- badges: end -->

## Description

Generates confidence intervals for standardized regression coefficients
using delta method standard errors for models fitted by `lm()`
as described in Yuan and Chan (2011: http://doi.org/10.1007/s11336-011-9224-6)
and Jones and Waller (2015: http://doi.org/10.1007/s11336-013-9380-y).

## Installation

You can install the CRAN release of `betaDelta` with:

```r
install.packages("betaDelta")
```

You can install the development version of `betaDelta` from
[GitHub](https://github.com/jeksterslab/betaDelta) with:

```r
if (!require("remotes")) install.packages("remotes")
remotes::install_github("jeksterslab/betaDelta")
```

## Example

In this example, a multiple regression model is fitted
using program quality ratings (`QUALITY`) as the regressand/outcome variable
and number of published articles attributed to the program faculty members (`NARTIC`),
percent of faculty members holding research grants (`PCTGRT`), and
percentage of program graduates who received support (`PCTSUPP`) as regressor/predictor variables
using a data set from 1982 ratings of 46 doctoral programs in psychology in the USA (National Research Council, 1982).
Confidence intervals for the standardized regression coefficients are generated
using the `BetaDelta()` function from the `betaDelta` package following Yuan and Chan (2011) and Jones and Waller (2015).

```{r}
#| message = FALSE
library(betaDelta)
```

```{r}
#| echo = FALSE
if (!exists("nas1982")) {
  try(
    data(
      "nas1982",
      package = "betaDelta"
    ),
    silent = TRUE
  )
}
df <- nas1982
```

```{r}
#| eval = FALSE
df <- betaDelta::nas1982
```

### Fit the regression model using the `lm()` function.

```{r}
object <- lm(QUALITY ~ NARTIC + PCTGRT + PCTSUPP, data = df)
```

### Estimate the standardized regression slopes and the corresponding sampling covariance matrix.

#### Multivariate Normal-Theory Approach

```{r}
BetaDelta(object, type = "mvn")
```

#### Asymptotic Distribution-Free Approach

```{r}
BetaDelta(object, type = "adf")
```

### References

Jones, J. A., & Waller, N. G. (2015).
The normal-theory and asymptotic distribution-free (ADF) covariance matrix
of standardized regression coefficients:
Theoretical extensions and finite sample behavior.
*Psychometrika*, *80*(2), 365–378.
https://doi.org/10.1007/s11336-013-9380-y

National Research Council. (1982).
*An assessment of research-doctorate programs in the United States: Social and behavioral sciences*.
https://doi.org/10.17226/9781.
Reproduced with permission from the National Academy of Sciences,
Courtesy of the National Academies Press, Washington, D.C.

Yuan, K.-H., & Chan, W. (2011).
Biases and standard errors of standardized regression coefficients.
*Psychometrika*, *76*(4), 670–690.
https://doi.org/10.1007/s11336-011-9224-6

## Documentation

See
[GitHub Pages](https://jeksterslab.github.io/betaDelta/index.html)
for package documentation.
