---
title: "betaDelta: Example Using the DiffBetaDelta Function"
author: "Ivan Jacob Agaloos Pesigan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{betaDelta: Example Using the DiffBetaDelta Function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To cite `betaDelta` in publications, please use:

Pesigan, I. J. A., Sun, R. W., & Cheung, S. F. (2023).
betaDelta and betaSandwich: Confidence intervals for standardized regression coefficients in R.
*Multivariate Behavioral Research*.
https://doi.org/10.1080/00273171.2023.2201277

Confidence intervals for
differences of standardized regression slopes
are generated using
the `DiffBetaDelta()` function from the `betaDelta` package.
In this example,
we use the data set and the model used in
[betaDelta: Example Using the BetaDelta Function](example_beta_delta.html).

```{r}
#| message = FALSE
library(betaDelta)
```

```{r}
#| echo = FALSE
if (!exists("nas1982")) {
  try(
    data(
      "nas1982",
      package = "betaDelta"
    ),
    silent = TRUE
  )
}
df <- nas1982
```

```{r}
#| eval = FALSE
df <- betaDelta::nas1982
```

## Fit the regression model using the `lm()` function.

```{r}
object <- lm(QUALITY ~ NARTIC + PCTGRT + PCTSUPP, data = df)
```

## Estimate the standardized regression slopes and the corresponding sampling covariance matrix.

#### Multivariate Normal-Theory Approach

```{r}
std_mvn <- BetaDelta(object, type = "mvn")
```

#### Asymptotic Distribution-Free Approach

```{r}
std_adf <- BetaDelta(object, type = "adf")
```

## Estimate differences of standardized regression slopes and the corresponding sampling covariance matrix.

```{r}
mvn <- DiffBetaDelta(std_mvn)
adf <- DiffBetaDelta(std_adf)
```

### summary

Summary of the results of `DiffBetaDelta()`.

```{r}
summary(mvn)
summary(adf)
```

### coef

Calculate differences of standardized regression slopes.

```{r}
coef(mvn)
coef(adf)
```

### vcov

Calculate the sampling covariance matrix of differences of standardized regression slopes.

```{r}
vcov(mvn)
vcov(adf)
```

### confint

Generate confidence intervals for differences of standardized regression slopes.

```{r}
confint(mvn, level = 0.95)
confint(adf, level = 0.95)
```

## References

National Research Council. (1982).
*An assessment of research-doctorate programs in the United States: Social and behavioral sciences*.
https://doi.org/10.17226/9781.
Reproduced with permission from the National Academy of Sciences,
Courtesy of the National Academies Press, Washington, D.C.

Pesigan, I. J. A., Sun, R. W., & Cheung, S. F. (2023).
betaDelta and betaSandwich: Confidence intervals for standardized regression coefficients in R.
*Multivariate Behavioral Research*.
https://doi.org/10.1080/00273171.2023.2201277
