---
title: "betaDelta: Example using the dif Method"
author: "Ivan Jacob Agaloos Pesigan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{betaDelta: Example using the dif Method}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this example, a multiple regression model is fitted
using program quality ratings (`QUALITY`) as the regressand/outcome variable
and number of published articles attributed to the program faculty members (`NARTIC`),
percent of faculty members holding research grants (`PCTGRT`), and
percentage of program graduates who received support (`PCTSUPP`) as regressor/predictor variables
using a data set from 1982 ratings of 46 doctoral programs in psychology in the USA (National Research Council, 1982).
Confidence intervals for differences of standardized regression slopes are generated
using the `dif()` method from the `betaDelta` package.

```{r}
#| message = FALSE
library(betaDelta)
```

```{r}
#| echo = FALSE
if (!exists("nas1982")) {
  try(
    data(
      "nas1982",
      package = "betaDelta"
    ),
    silent = TRUE
  )
}
df <- nas1982
```

```{r}
#| eval = FALSE
df <- betaDelta::nas1982
```

## Fit the regression model using the `lm()` function.

```{r}
object <- lm(QUALITY ~ NARTIC + PCTGRT + PCTSUPP, data = df)
```

## Estimate the standardized regression slopes and the corresponding sampling covariance matrix.

#### Multivariate Normal-Theory Approach

```{r}
std_mvn <- BetaDelta(object, type = "mvn")
```

#### Asymptotic Distribution-Free Approach

```{r}
std_adf <- BetaDelta(object, type = "adf")
```

## Methods

### diff

```{r}
mvn <- dif(std_mvn)
adf <- dif(std_adf)
```

### summary

Summary of the results of `dif()`.

```{r}
summary(mvn)
summary(adf)
```

### coef

Calculate differences of standardized regression slopes.

```{r}
coef(mvn)
coef(adf)
```

### vcov

Calculate the sampling covariance matrix of differences of standardized regression slopes.

```{r}
vcov(mvn)
vcov(adf)
```

### confint

Generate confidence intervals for differences of standardized regression slopes.

```{r}
confint(mvn, level = 0.95)
confint(adf, level = 0.95)
```

## References

National Research Council. (1982).
*An assessment of research-doctorate programs in the United States: Social and behavioral sciences*.
https://doi.org/10.17226/9781.
Reproduced with permission from the National Academy of Sciences,
Courtesy of the National Academies Press, Washington, D.C.
